### 2019-04-11 5_evaluation.tex
Final updates for paper submission.

Not all cores are required to saturate memory bandwidth. As a result,
systems that reserve one or more cores are able to hit 100\% of peak
performance, unlike with compute-bound kernels. Otherwise the
performance curves are similar. We are currently investigating the
performance of Charm++.

% FIXME: why is Charm++ slow?

@@

The ratio in METG between 0 and 3 dependencies per task ranges from
$1.01\times$ to $16\times$ (median $2.9\times$). From 1 to 3
dependencies, the ratio varies from $0.54\times$ to $7.3\times$ (median
$1.8\times$). The difference is most pronounced in systems that
perform runtime work inline. For example, MPI achieves an METG of 390
ns with 0 dependencies, but this rises to 4.6 \textmu{}s with 3 dependencies,
a factor of $12\times$ increase. This is unsurprising as in the case
of 0 dependencies, no \lstinline[language=C++]{MPI_Isend} calls are
issued at all, so MPI has nothing to do aside from executing kernels
as quickly as possible. For this reason, we recommend evaluating the performance of
programming systems under realistic workloads, rather than with
trivial dependencies.

@@

One advantage of systems with asynchronous execution capabilities is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under load imbalance where each task's duration is multiplied by a uniform random variable between [0,~1). The task durations are generated with a deterministic
pseudo random number generator with a deterministic seed to ensure
identical task durations for all systems.

>>>>

Not all cores are required to saturate memory bandwidth. As a result,
systems that reserve one or more cores are able to hit 100\% of peak
performance, unlike with compute-bound kernels. Otherwise the
performance curves are similar. We are currently investigating the
performance of Charm++ and Regent.

% FIXME: why are Charm++ and Regent slow?

@@

%% From 1 to 3
%% dependencies, the ratio varies from $0.54\times$ to $7.3\times$ (median
%% $1.8\times$).

The ratio in METG between 0 and 3 dependencies per task ranges from
$1.01\times$ to $16\times$ (median $2.9\times$). The difference is most pronounced in systems that
perform runtime work inline. For example, MPI achieves an METG of 390
ns with 0 dependencies, but this rises to 4.6 \textmu{}s with 3 dependencies,
a factor of $12\times$ increase. This is unsurprising as in the case
of 0 dependencies, no \lstinline[language=C++]{MPI_Isend} calls are
issued at all, so MPI has nothing to do aside from executing kernels
as quickly as possible. For this reason, we recommend evaluating the performance of
programming systems under realistic workloads, rather than with
trivial dependencies.

@@

One advantage of systems with asynchronous execution capabilities is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under load imbalance where each task's duration is multiplied by a uniform random variable between [0,~1). The task durations are generated with a deterministic
pseudo random number generator with a consistent seed to ensure
identical task durations for all systems.
